Experiment 1 of 4

### 2016-09-24 experiments/e1/writeup/e1.Rmd
I dropped the maximal models into commented out code

```{r computeLmerModels, cache = TRUE, tidy=FALSE}
rt.lmer.1 <- lmerTest::lmer(
  data=rtdata, logrt ~ c_Vgn * c_Gap + (c_Vgn * c_Gap|subject))
rt.lmer.2 <- lmerTest::lmer(
  data=rtdata, logrt ~ c_Vgn * c_Gap + c_Ord + c_Qty + (c_Vgn * c_Gap + c_Ord + c_Qty | subject))
ac.lmer.1 <- lme4::glmer(
  data = erdata, error ~ c_Vgn * c_Gap + (c_Vgn * c_Gap | subject), 
  family="binomial", control = glmerControl(optimizer = "bobyqa"))
ac.lmer.2 <- lme4::glmer(
  data = erdata, error ~ c_Vgn * c_Gap + c_Ord + c_Qty + (c_Vgn * c_Gap + c_Ord + c_Qty | subject), 
  family="binomial", control = glmerControl(optimizer = "bobyqa"))
```

@@

for (i in ncol(x)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}
print(
  xtable(
    align='lrrrrr', 
    digits=c(0,  2,2,2,2,3),
    x,
    caption="Simple response time model"), 
    caption.placement="top", 
  type='html')
```

```{r tableRTmodelMaximal, results='asis', echo=FALSE, cache=TRUE}
x = as.data.frame(format(summary(rt.lmer.2)$coef, scientific=FALSE), stringsAsFactors = FALSE)

for (i in ncol(x)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}
print(
  xtable(
    align='lrrrrr', 
    digits=c(0,  2,2,2,2,3),
    x,
    caption="Maximal response time model"), 
    caption.placement="top", 
  type='html')
```

@@

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(summary(
    ac.lmer.1)$coefficients,
         digits=3, 
         caption="Simple error rates model"),
         caption.placement="top", type='html')
```

```{r tableErrorModelMaximal, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(
    digits=3, summary(
      ac.lmer.2)$coefficients,
             caption="Maximal error rates model"),
             caption.placement="top", type='html')
```

>>>>

```{r computeLmerModels, cache = TRUE, tidy=FALSE}
rt.lmer.1 <- lmerTest::lmer(
  data=rtdata, logrt ~ c_Vgn * c_Gap + (c_Vgn * c_Gap|subject))

ac.lmer.1 <- lme4::glmer(
  data = erdata, error ~ c_Vgn * c_Gap + (c_Vgn * c_Gap | subject), 
  family="binomial", control = glmerControl(optimizer = "bobyqa"))
```

@@

for (i in ncol(x)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}
print(
  xtable(
    align='lrrrrr', 
    digits=c(0,  2,2,2,2,3),
    x,
    caption="Response time model"), 
    caption.placement="top", 
  type='html')
```

@@

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(summary(
    ac.lmer.1)$coefficients,
         digits=3, 
         caption="Error rates model"),
         caption.placement="top", type='html')
```

<!-- ```{r} -->
<!-- rt.lmer.2 <- lmerTest::lmer( -->
<!--   data=rtdata, logrt ~ c_Vgn * c_Gap + c_Ord + c_Qty + (c_Vgn * c_Gap + c_Ord + c_Qty | subject)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ac.lmer.2 <- lme4::glmer( -->
<!--   data = erdata, error ~ c_Vgn * c_Gap + c_Ord + c_Qty + (c_Vgn * c_Gap + c_Ord + c_Qty | subject),  -->
<!--   family="binomial", control = glmerControl(optimizer = "bobyqa")) -->
<!-- ``` -->

<!-- ```{r tableRTmodelMaximal, results='asis', echo=FALSE, cache=TRUE} -->
<!-- x = as.data.frame(format(summary(rt.lmer.2)$coef, scientific=FALSE), stringsAsFactors = FALSE) -->

<!-- for (i in 1:(ncol(x)-1)) { -->
<!--   for (j in 1:nrow(x)) { -->
<!--     x[j,i] <-  substr(x[j,i], start=1, stop=7) -->
<!--   } -->
<!-- } -->

<!-- for (i in 1:(ncol(x)-1)) { -->
<!--   x[,i] <- as.numeric(x[,i]) -->
<!-- } -->

<!-- for (i in ncol(x)) { -->
<!--   for (j in 1:nrow(x)) { -->
<!--     x[j,i] <-  substr(x[j,i], start=1, stop=7) -->
<!--   } -->
<!-- } -->
<!-- print( -->
<!--   xtable( -->
<!--     align='lrrrrr',  -->
<!--     digits=c(0,  2,2,2,2,3), -->
<!--     x, -->
<!--     caption="Maximal response time model"),  -->
<!--     caption.placement="top",  -->
<!--   type='html') -->
<!-- ``` -->

<!-- ```{r tableErrorModelMaximal, results='asis', cache=TRUE, echo=FALSE} -->
<!-- print( -->
<!--   xtable( -->
<!--     digits=3, summary( -->
<!--       ac.lmer.2)$coefficients, -->
<!--              caption="Maximal error rates model"), -->
<!--              caption.placement="top", type='html') -->
<!-- ``` -->
